\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-04-02 paper/paper.tex
Additions from our meeting
Paper edits.

\newpage
\spacingset{1.45} % DON'T change the spacing!
\section{Introduction}
We present an approach to modeling failure data with heavy censoring, multiple censoring and multiple truncation. We present the generalized limited failure population model of Meeker and Hong which provides a generative model for failure distributions characterized by a "bathtub" hazard function (citation). This model may provide an adequate fit to failures of complex systems by differentiating between early and late types of failures as well as the propensity toward early failure. We discuss the case where the data are grouped, suggesting that we might expand the model, accounting for differences among groups. We show that by modeling the data hierarchically, we can deal with groups of various sizes by borrowing information across groups. We illustrate our approach on a large set of failure data for hard disk drives made available by Backblaze (citation).

\subsection{Background}

Hard drive failure is the primary cause of data loss and or damage \cite{harris}.  In addition to the cost of repairing a broken hard drive, lost or corrupted data can have major economic consequences for businesses, researchers, and consumers \cite{smith}.  To protect against hard drive failure multiple companies now offer backup storage.  One of the major online backup companies is Backblaze.  While selling storage space is Backblaze's main business, since 2013 it has been collecting data on hard drives operating at its facility.  The purpose is to provide consumers and businesses with reliability information on different hard drive brands and models.  The hard drives continuously spin in controlled storage pods where they run until failure.  When a hard drive fails it is permanently removed, and new hard drives are regularly added to the storage pods.  In addition, the number of storage pods is increasing as Backblaze adds new hard drive brands to the sample.  Every quarter Backblaze makes its data publicly available through their website \cite{backblaze}. In addition, Backblaze publishes summary statistics of the different hard drive models currently operating.  No other analysis or modeling of the failure data is provided; however, Backblaze does encourage the public to further analyze its data, which for this paper goes through the first quarter of 2016.

@@

\section{Data}
As of the first quarter of 2016, Backblaze was collecting data on 63 different hard drive models.  Some drive models have been running since 2013, while others have been added at a later date.  There are a total of 75,297 hard drives running.  The distribution of drives by model varies: some models have only 1 drive in testing; the maximum number of drives running for a specific drive model is 35,860.  We can also look at the distribution of total number of failures and total time on test across all drive models.  As seen below, some drive models contain a lot of information, while others have few failures or a little time in operation. [INSERT FIGURE 1]. \\

@@

\section{GFLP Model}
\subsection{Motivation}
We suggest the motivation for the GFLP model in the Data Section.  Perhaps expand on this a little more?

\subsection{Model}
Write out the full Bayes hierarchical model for the GFLP model

>>>>

\newpage
\spacingset{1.45} % DON'T change the spacing!
\section{Introduction}
We present an approach to modeling failure data with heavy censoring, multiple censoring and multiple truncation. We present the generalized limited failure population model (GFLP) of Chan and Meeker which provides a generative model for failure distributions characterized by a "bathtub" hazard function (citation). This model may provide an adequate fit to failures of complex systems by differentiating between early and late types of failures as well as the propensity toward early failure. We discuss the case where the data are grouped, suggesting that we might expand the model, accounting for differences among groups. We show that by modeling the data hierarchically, we can deal with groups of various sizes by borrowing information across groups. We illustrate our approach on a large set of failure data for hard disk drives made available by Backblaze (citation).

\subsection{Background}
Products can frequently fail due to more than one cause.  For example, there are many parts in a washing machine that can break and cause the whole machine to fail.  Decorative tree lighting can fail if one bulb in the chain burns out.  The general name for such products is a series system where the lifetime of the product is the minimum failure time across $s$ different components or risks \cite{nelson}.  A common assumption is the times to failure for each risk, $s$, are statistically independent.  Thus, the overall reliability of a unit can be modeled using the product rule across all $s$ risks.  The GFLP model is a special case of the $s$ independent competing risks model with 2 modes of failure: defects and wearout.  Sometimes the cause of the failure is know; but more often the observations do not contain any information about the failure mode \cite{chan}.  The GFLP model was first used to describe the early and late failure modes of CB radios.  No failure information was available for this data, which made fitting the model a challenge using maximum likelihood estimation.  Other authors, for example, Basu et al., used a Bayesian approach to fit the GFLP model to masked failure data from an engineering system \cite{basu}.  More recently, Ranjan et al. considered a competing risk model for infant mortality and wearout as a mixture of Weibull and exponential failure distributions \cite{ranjan}.

@@

\section{Data}
Backblaze is a company that offers backup storage to protect against hard drive failure.  While selling storage space is Backblaze's main business, since 2013 it has been collecting data on hard drives operating at its facility.  The purpose is to provide consumers and businesses with reliability information on different hard drive brands and models.  The hard drives continuously spin in controlled storage pods where they run until failure.  When a hard drive fails it is permanently removed, and new hard drives are regularly added to the storage pods.  In addition, the number of storage pods is increasing as Backblaze adds new hard drive brands to the sample.  Every quarter Backblaze makes its data publicly available through their website \cite{backblaze}. In addition, Backblaze publishes summary statistics of the different hard drive models currently operating.  No other analysis or modeling of the failure data is provided; however, Backblaze does encourage the public to further analyze its data, which for this paper goes through the first quarter of 2016.

As of the first quarter of 2016, Backblaze was collecting data on 63 different hard drive models.  Some drive models have been running since 2013, while others have been added at a later date.  There are a total of 75,297 hard drives running.  The distribution of drives by model varies: some models have only 1 drive in testing; the maximum number of drives running for a specific drive model is 35,860.  We can also look at the distribution of total number of failures and total time on test across all drive models.  As seen below, some drive models contain a lot of information, while others have few failures or a little time in operation. [INSERT FIGURE 1]. \\

@@

\section{GFLP Model}
\subsection{Model}
Write out the full Bayes hierarchical model for the GFLP model
\subsubsection{Varying proportion defective}
\subsubsection{Varying wearout mode}
\subsubsection{Varying defective failure model}
